Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2019-05-11 awipev-CO2.Rmd

f <- as.data.frame(table(d_all$at))
sum(f$Freq)
# Number of outliers removed in the dataset
# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))
```

@@

#### **Final TA re-calculated data (Salinity relationship)**
```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2450)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
titre <- "Contros AT vs Calculated AT"
fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
    ```

@@

@@

print(plot_offset_dur)
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

>>>>

f <- as.data.frame(table(d_all$at))
sum(f$Freq)
# Number of outliers removed in the dataset
# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))

#plot for POSTER june 2019
#plot of S/T
poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 ), aes(x=datetime,y=temp_fb)) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Temperature (°C)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_temp)
ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")

poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb)) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Time", y="Salinity (PSU)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_sal)
ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")

@@

#### **Final TA re-calculated data (Salinity relationship)**
```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2450)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

#plot for POSTER june 2019
#plot of TA calculated from S + discrete
p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  geom_point(aes(y=at, fill= "Reference measured samples"), col="red") +
  labs(x = "Time", y = "Calculated TA from salinity (µmoles/kg)") +
  scale_x_datetime(date_minor_breaks ="1 month")+
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(p_at_sal)
ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")

@@

at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
titre <- "Contros AT vs Calculated AT"
fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")

#plot for POSTER june 2019
#plot of TA VS calculated
poster_at_atcal <- ggplot(data = at_nov_2018%>%dplyr::filter(at_calc > 2000), aes(x=at_calc,y=AT_filtered_despike,col="TA calculated from salinity") ) +
  geom_point(col="blue", size=0.5 )+
  labs(x = "Calculated TA", y = "Calculated TA from salinity (µmoles/kg)") +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_at_atcal)
ggsave(paste0("figures/poster_at_atcal.png"), width= 30, height=10, poster_at_atcal, units="cm")
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

#plot for POSTER june 2019
#plot of pCO2
poster_pco2 <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
  geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
  labs(x = "Time", y = expression(~italic(p)~CO[2]~"(µatm)")) +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
print(poster_pco2)
ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
    ```

@@

#plot for POSTER june 2019
#plot of pH seafet
poster_ph <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Reference measured samples"), col="red" )+
  labs(x = "Time", y = expression(pH[T]~seaFET)) +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())

print(poster_ph)
ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")

# RANGE of pH
d_all<- d_all%>%
  dplyr::mutate(year = year(datetime))
range <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
)
quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
plot_range_sf <-  
  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_sf)
ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")

@@

print(plot_offset_dur)

#plot for POSTER june 2019
#plot of pH durafet
poster_dur <- ggplot( ) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Reference measured samples"), col="red" )+
  labs(x = "Time", y = expression(pH[T]~durafet)) +
  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())

print(poster_dur)
ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")

# RANGE of pH
range_dur <- tbl_df(
  d_all %>%
  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
)
quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)

# Per month
range_month <-
  range_dur %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))

size_point <- 0.4 # size of data points
plot_range_dur <-  
  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank())
print(plot_range_dur)
ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
